The Privacy of Private Browsing

### 2013-12-16 finalproject/paper.tex
cleaned code, wrote last paragraph

	\subsection{Proof of Concept: Parsing SQLite Databases and Browser Memory}
	% find paper that had the thing about no last visited date and cite
	As an example of the persistence of some of these private browsing 
	shortcomings, two Python scripts were written to accompany this paper.
	The first parses the SQLite databases of Mozilla Firefox to look for 
	private browsing artifacts. There are two built-in artifact searches. It 
	will print any cookies created within the last hour; if private browsing is
	currently in use, some cookies may show up here before being removed upon
	browser termination. Additionally, URLs that have a nonzero access count
	but an unspecified last visit time will be printed. It cannot be easily
	determined when these websites were visited, but it is likely that it was
	during a private browsing session. Upon manual review of the URLs retrieved 
	from this database, URLs visited more recently during a private browsing 
	session appeared at the bottom of the list. The 
	\href{https://addons.mozilla.org/en-US/firefox/addon/sqlite-manager}
	{SQLite Manager} extension for Firefox was used to discover these possible
	artifact sources before a programmatic solution was implemented.

	The second script retrieves the contents of the memory segments associated
	with a running Firefox or Chrome process.
	%Finish this

>>>>

	\subsection{Proof of Concept: Parsing SQLite Databases and Browser Memory}
	As an example of the persistence of some of these private browsing 
	shortcomings, two Python scripts were written to accompany this paper.
	The first parses the SQLite databases of Mozilla Firefox to look for 
	private browsing artifacts. There are two built-in artifact searches. It 
	will print any cookies created within the last hour; if private browsing is
	currently in use, some cookies may show up here before being removed upon
	browser termination. Additionally, URLs that have a nonzero access count
	but an unspecified last visit time will be printed. It cannot be easily
	determined when these websites were visited, but it is likely that it was
	during a private browsing session. Upon manual review of the URLs retrieved 
	from this database, URLs visited more recently during a private browsing 
	session appeared at the bottom of the list. The 
	\href{https://addons.mozilla.org/en-US/firefox/addon/sqlite-manager}
	{SQLite Manager} extension for Firefox was used to discover these possible
	artifact sources before a programmatic solution was implemented.

	The second script retrieves the contents of the memory segments associated
	with a running Firefox or Chrome process. String literals in the browser's
	memory are then logged to an output file, separated by browser.
	Additionally, potentially interesting memory contents (currently URLs, but
	could easily be modified to include other items of interest) are printed to
	the terminal. This was accomplished using the 
	\href{http://winappdbg.sourceforge.net/}{WinAppDbg} module.
